\documentclass[a4paper,11pt]{article}

\usepackage[%
    top=0.75in,%
    left=1.2in,%
    right=1.2in,%
    bottom=0.75in%
]{geometry}

\usepackage[defaultsans]{opensans}
\usepackage{sourcesanspro}
\usepackage{charter}
\usepackage{hyperref}
\pagenumbering{gobble}

\usepackage[%
    tracking=true,%
    letterspace=150,%
    kerning=true,%
    selected=true%
]{microtype}

\usepackage{titlesec}

\titleformat{\section}%
{\scshape\normalsize\sffamily}{}{0pt}%
{\rule{\textwidth}{0.5pt}\\}%
{\bigskip}%

% -- Convenience --
\newcommand{\hdr}[2]{{\raggedright\Large #1 \hfill #2}}
\newcommand{\itm}{\item[-]}

\begin{document}

% -- Mast --
\begin{center}
\begin{scshape}
{\huge\sffamily Rohan Mahendraker}\\
\medskip
\textsf{(+44) 1234 567890  :  rohan@mahendraker.com}
\end{scshape}
\end{center}

% -- Body --
\section{Education}
\hdr{King's Business School}{2020 -- 2023}
\begin{itemize}
	\itm Received First Class Honours BSc. degree in Accounting \& Finance.
	\itm Received letter of commendation from the Dean of Faculty for academic excellence.
	\itm Expected to receive qualification of First with Honours.
	\itm Class Rank: 4th.
\end{itemize}
\medskip
\hdr{International School of Helsinki}{2010 -- 2019}
\begin{itemize}
    	\itm International Baccalaureate Diploma: 40 points.
	\itm Class rank: 1st, Global Percentile: 95th.
	\itm Graduated each year with Headmaster's Honours.
\end{itemize}


\section{Work Experience}
\hdr{Venyu}{2023 - Ongoing}\\[2mm]
\emph{\large CTO/Cofounder}
\begin{itemize}
	\itm Cofounded Venyu – a one-stop-shop for corporate event booking.
	\itm Used React/React Native for frontend, Firebase for backend, and Figma for UI.
    	\itm £50k+ in GMV, customers include PwC, easyJet, and NatWest.
\end{itemize}
\bigskip

\hdr{Teuf avoin yhti\"{o}}{2017 - 2021}\\[2mm]
\emph{\large Founder}
\begin{itemize}
	\itm Founded and led a profitable 3-person event/artist management company.
    	\itm Coordinated and managed logistics for nightlife events with 300+ attendees.
	\itm Developed a Flutter/Firebase mobile app to distribute nightlife promo content.
	\itm Partnered with Rekom Group – the largest nightlife provider in Scandinavia.
	\itm Managed the careers of Vic Versa, Ninoz and Rocky9 (400k+ streams combined). 

\end{itemize}
\section{Skills}
\hdr{Software Development}{}\\[2mm]
\emph{\large Python, Dart, HTML/CSS, JavaScript/TypeScript, Firebase, Docker, Figma}
\smallskip
\begin{itemize}
	\itm Developed a Docker-ized invoice generation API for an ERP firm using Django.
	\itm Wrote a web-services sales lead generator that scraped the Finnish Trade Register API.
	\itm Deployed a NFT generative art project on the Ethereum Blockchain using Python.
\end{itemize}

\end{document}

